Artin Group Presentations Arising from Cluster Algebras

### 2014-08-12 Paper.tex

\begin{defn}
\cite[Beginning of section 1.2]{C06}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i},$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } M_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

@@

>>>>

\begin{defn}
\cite[Beginning of section 1.2]{C06}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i},$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \forall i,j \text{ with } M_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

One of the most well-known Artin groups is the braid group on n strands, which was shown to have an Artin group structure in \cite{FN61}. The associated Coxeter group is the symmetric group $S_{n}$.

@@

\section{Acknowledgements}
\thanks{This work was supported by the RTG grant NSF/DMS-1148634. We'd also like to thank the University of Minnesota School of Mathematics for hosting us, and we'd like to thank Gregg Musiker and Emily Gunawan for their useful comments on our work.
